---
title: "Cabbages"
author: "Gema Garcia"
date: "June 5 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
# Load required library
library(ggplot2)

# Create the box plot with centered and bigger title
ggplot(veggy, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  xlab("Cult") +
  ylab("Vitamin C") +
  ggtitle("Box Plot of Vitamin C by Cult") +
  theme(plot.title = element_text(hjust = 0.5, size = 20))

```


Looking at the 2 boxes we could see the c52 box is higher and if we were to put them in the same column, they would not overlap. The middle 50% is higher in the c52 than the middle 50% of c39. We think we will find a statistical difference within these two methods.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```


The average amount of VitC in c39 is about 51.0. While in c52 the average is about 64.5. The bottom of the c52 box is bigger because in Q1 it is 58 which is larger than the top of the box of c39's 46 in Q1. This helps me see all the data in numerical form.



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```


The probability of getting the result we just got is .00000003405 and it is very small. Which is exactly what we got and it was possible because we did the work to see that there was a big difference.





# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


We used chatGPT to help us get the code so we could make our box plot.Which then lead us to inspect the data and write our conclusions. We went from copying codes in our numerical cat and then pasting it here. Changing what it would say to better fit our data and then we would run it.Each time we got our data in different forms and just formed conclusions each time to explain it better.  